Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-14 acknowledgments.tex
Adding Gabriel Altay to the list of enzo contributors.

>>>>

The \enzo\ collaboration would like to acknowledge the following
scientists, who have made contributions to the \enzo\ codebase at some
point during their research career: Gabriel Altay, Brian Crosby,
Elizabeth Harper-Clark, Daegene Koh, Eve Lee, Pascal Paschos, Carolyn
Peruta, Alex Razoumov, Munier Salem, and Rick Wagner.
